### 2015-11-30 paper.tex
init

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{ Chinese Poem Generator from Image}

\author{Kelei Cao\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Dichen Qian\\
Tsinghua University \\
Computer Science \& Technology\\
{\tt\small nathenqian@gmail.com}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   	Chinese poem is very popular in China, for it's meaningful, convenience and gentle. It is very common in China that children can recite lot's of poems before primary school. 
	In Chinese parmary school, most Chinese teacher will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.

	As the innovation of neural network has springed up these years, it's very interesting for computer whether they can make sentences based on an image. To make the thing even fantastic, we want to make the computer to generate the poem based on an specific image.

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Deep learning has been proven in recent years to be an extremely useful tool for discriminative tasks. Through layers of linear transforms combined with nonlinearities, these systems learn to transform their input into an ideal representation across which we can draw clear decision boundaries. However It remains to be seen how this success might play out in the field of generative models. For computer, create the news based on the things it has learned must be the next generation.

In this paper, we will develop a generative models that can recognize the image, and generate the poem based on the image. This is very basic for people, but hard for computer.
%-------------------------------------------------------------------------
\subsection{Problem Statement}
This problem is a generative problem. The generative models should generate the poem that base on an specific image, which means that the poem should describe the image .

The input is an image, contains some information and people can easily find out what the emotion it convey. The graph contains with different emotion is best for both people and computer to create the poem.

The output should be the beautiful poem that it's meaning is closed to this image.

\subsection{Plan}
\subsubsection{Image to Sentence}
The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.
\subsubsection{English to Chinese}
The sentence is English, so we need to change it from English to Chinese so that we can process our next step.
\subsubsection{Sentence to Poem}
The second part of this problem is to generate the poem base on the sentence. What need to do is extracting the feature from the sentence and use them to generate the poem.

\section{Related Work}

%-------------------------------------------------------------------------

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2015 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2015-12-01 paper.tex
remove

@@
 %\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\setcounter{page}{1}
 \begin{document}
@@
 
-In this paper, we will develop a generative models that can recognize the image, and generate the poem based on the image. This is very basic for people, but hard for computer.
+In this paper, we will develop a generative models that can recognize the image, extract the feature in the image, and generate the poem based on the image.
+This is very basic for people, but hard for computer.
+In some sense, we want to explore the ability of computer.
 %-------------------------------------------------------------------------
 \subsection{Problem Statement}
-This problem is a generative problem. The generative models should generate the poem that base on an specific image, which means that the poem should describe the image .
-
-The input is an image, contains some information and people can easily find out what the emotion it convey.
+This problem is a generative problem.
+The generative models should generate the poem that base on an specific image, which means that the poem should describe the image.
+For this purpose, the input image must contains some information and people can easily find out what the emotion it convey.
 The graph contains with different emotion is best for both people and computer to create the poem.
@@
 
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the CVPR70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-
-FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the CVPR 2015 web page for a discussion
-of the use of color in your document.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
-
 \end{document}

### 2015-12-01 paper.tex
modify

@@
 Computer Science \& Technology\\
-{\tt\small firstauthor@i1.org}
+{\tt\small ckl13@mails.tsinghua.edu.cn}
 % For a paper whose authors are all at the same institution,
@@
 
-\subsection{Plan}
-\subsubsection{Image to Sentence}
+\section{Related Work}
+	Generating poem is popular in recent years, and there are many people research on it.
+On the other hand, explain image with sentence has also made great progress after deep learning widely used.
+Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
+\section{Plan}
+\subsection{Image to Sentence}
 The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.
-\subsubsection{English to Chinese}
-The sentence is English, so we need to change it from English to Chinese so that we can process our next step.
-\subsubsection{Sentence to Poem}
-The second part of this problem is to generate the poem base on the sentence. What need to do is extracting the feature from the sentence and use them to generate the poem.
 
-\section{Related Work}
+The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L.
+Yuille : Explain Images with Multimodal Recurrent Neural Networks.}.
+We use a multimodal Recurrent Neural Networks (m-RNN) model to address both the task of generating novel sentences descriptions for images, and the task of image and sentence retrieval.
+The whole m-RNN architecture contains a language model part, an image part and a multimodal part.
+The language model part learns the dense feature embedding for each word in the dictionary and stores the semantic temporal context in recurrent layers.
+The image part contains a deep Convulutional Neural Network (CNN) \footnote{A.
+Krizhevsky, I.
+Sutskever, and G.
+E.
+Hinton.
+Imagenet classification with deep convolutional neural networks.
+In NIPS, pages 1097–1105, 2012.} which extracts image features.
 
+\subsection{Translate and Extract}
+Now we get the sentence, as to generate the meaningful poetry, we need to extract keywords from the sentences.
+We can use a translation process to deal the sentence and only use the words that appears in Chinese poetry dataset that we used in poem generator.
+
+\subsubsection{Poem generator}
+	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints.
+We use a language model to rank the generated candidates and select the best ranked one as the first line in the poem.
+In implementation, we employ a character-based recurrent neural network language model.
+	And after that, we generate the rest poem lines with original lines.
+Convert lines $s_1$...$s_i$ into vectors $v_1$...$v_i$ with a convolutional sentence model (CSM).
+Next, a recurrent context model (RCM) takes $v_1$...$v_i$ as input and outputs $u_{j,i}$.Finally, $u_{1,i}$, $u_{2,i}$,...,$u_{j,i}$ and the first $j$ characters $w_1$...$w_j$ in line $s_{i+1}$ serve as input to a recurrent generation model (RGM) which estimates $P(w_{j+1} = k | w_{1:j} ,s_{1:i} )$ with $k\in V$, the probability distribution of the $j+1$ th character over all words in the vocabulary $V$.
 %-------------------------------------------------------------------------
-
+\section{Dataset}
+The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image. The other is Chinese Poetry corpus.
+\section{Intermediate Result}
+We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good idea and gave some advices.
+We will soon try to use theano to implement our idea, for this week is the deadline of building a cpu.
 \end{document}

### 2015-12-01 paper.tex
finish

@@
 \begin{abstract}
-   	Chinese poem is very popular in China, for it's meaningful, convenience and gentle. It is very common in China that children can recite lot's of poems before primary school. 
-	In Chinese parmary school, most Chinese teacher will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.
+   	Chinese poem is very popular in China, for it's meaningful, outstanding and gentle.
+It is very common in China that children can recite lot's of poems before primary school.
+As a part of language, poem can represent the Chinese culture totally.
+	In Chinese primary school, most Chinese teachers will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.
 
@@
 
-In this paper, we will develop a generative models that can recognize the image, extract the feature in the image, and generate the poem based on the image.
+In this paper, we will develop a generative model that can recognize the image, extract the features in the image, and generate the poem based on the image.
 This is very basic for people, but hard for computer.
-In some sense, we want to explore the ability of computer.
+In some sense, we want to explore the speaking ability of computer.
 %-------------------------------------------------------------------------
 \subsection{Problem Statement}
-This problem is a generative problem.
-The generative models should generate the poem that base on an specific image, which means that the poem should describe the image.
+This problem is a generative problem. The generative model should generate the poem that base on an specific image, which means that the poem should describe the image.
+
 For this purpose, the input image must contains some information and people can easily find out what the emotion it convey.
-The graph contains with different emotion is best for both people and computer to create the poem.
+The graph contains with different emotion and things is best for both people and computer to create the poem.
 
 The output should be the beautiful poem that it's meaning is closed to this image.
+There are also some standards to judge whether the poem is good or not.
+The standard includes the atmosphere contained in the poem, and the meaning of the poem.
+Sounds of the poem is another factor which influence the performance a lot.
 
@@
 	Generating poem is popular in recent years, and there are many people research on it.
-On the other hand, explain image with sentence has also made great progress after deep learning widely used.
+On the other hand, explaining image with sentence has also made great progress after deep learning widely used.
 Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
@@
 The language model part learns the dense feature embedding for each word in the dictionary and stores the semantic temporal context in recurrent layers.
-The image part contains a deep Convulutional Neural Network (CNN) \footnote{A.
+The image part contains a deep Convolutional Neural Network (CNN) \footnote{A.
 Krizhevsky, I.
@@
 
-\subsubsection{Poem generator}
+\subsection{Poem generator}
 	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints.
@@
 \section{Dataset}
-The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image. The other is Chinese Poetry corpus.
+The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image.
+
+The other is Chinese Poetry corpus to train for the generate part.
 \section{Intermediate Result}
-We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good idea and gave some advices.
-We will soon try to use theano to implement our idea, for this week is the deadline of building a cpu.
+We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good  and practical reasonable idea and gave some advices.
+We will soon try to use theano to implement our idea. Recent three weeks is the deadline of building a cpu so we don't have enough time to try our idea.
 \end{document}

### 2015-12-01 paper.tex
fix some syntax bug

@@
 \begin{abstract}
-   	Chinese poem is very popular in China, for it's meaningful, outstanding and gentle.
-It is very common in China that children can recite lot's of poems before primary school.
-As a part of language, poem can represent the Chinese culture totally.
-	In Chinese primary school, most Chinese teachers will teach children how to make sentences based on what they look. In addition, it's a way to cultivate the ability of communication for children.
+   	Chinese poem is very popular in China, for it's meaningful, outstanding and elegant.
+It is quite common in China that children can recite lots of poems before primary school.
+As a part of language, poem represents Chinese culture and history.
+	In Chinese primary school, most Chinese teachers will teach children how to make sentences based on what they see and hear. In addition, it's a way to cultivate the kids' ability to communicate.
 
-	As the innovation of neural network has springed up these years, it's very interesting for computer whether they can make sentences based on an image.
+	As the innovation of neural network has been booming these years, it's very interesting for computer whether they can make sentences based on an image.
 To make the thing even fantastic, we want to make the computer to generate the poem based on an specific image.
@@
 Deep learning has been proven in recent years to be an extremely useful tool for discriminative tasks.
-Through layers of linear transforms combined with nonlinearities, these systems learn to transform their input into an ideal representation across which we can draw clear decision boundaries.
-However It remains to be seen how this success might play out in the field of generative models.
-For computer, create the news based on the things it has learned must be the next generation.
+Through layers of linear transformation combined with nonlinearities, these systems learn to transform their input into an ideal representation across which we can draw clear decision boundaries.
+However, it remains to be discussed how this success might play out in the field of generative models.
+For computer, creating the new things based on what it has learned must be the magnet in the next generation.
 
 In this paper, we will develop a generative model that can recognize the image, extract the features in the image, and generate the poem based on the image.
-This is very basic for people, but hard for computer.
+This is very basic for people, but rather hard for computer.
 In some sense, we want to explore the speaking ability of computer.
@@
 \subsection{Problem Statement}
-This problem is a generative problem. The generative model should generate the poem that base on an specific image, which means that the poem should describe the image.
+This problem is a generative problem. The generative model will generate the poem that is based on an specific image, which means that the poem should describe the image.
 
-For this purpose, the input image must contains some information and people can easily find out what the emotion it convey.
-The graph contains with different emotion and things is best for both people and computer to create the poem.
+For this purpose, the input image must contain some information and people can easily find out what emotions it convey.
+We presuppose that the graph is rich in emotion and is suitable for both human and computer to create the poem.
 
-The output should be the beautiful poem that it's meaning is closed to this image.
+The output should be the beautiful poem whose meaning is close to this image.
 There are also some standards to judge whether the poem is good or not.
-The standard includes the atmosphere contained in the poem, and the meaning of the poem.
-Sounds of the poem is another factor which influence the performance a lot.
+The standard includes the atmosphere showed in the poem and the meaning of the poem.
+Rhyme is another factor which influence the performance a lot.
 
 \section{Related Work}
-	Generating poem is popular in recent years, and there are many people research on it.
-On the other hand, explaining image with sentence has also made great progress after deep learning widely used.
-Our approach is a combination of above two aspects, we select two methods that performing well in corresponding aspects, and try to get a fantastic result.
+	Generating poem is popular in recent years, and there are abundant research on it.
+On the other hand, explaining image with words has also made great progress after deep learning is widely used.
+Our approach is a combination of the above two aspects, we select two methods that performing well in corresponding aspects, and try to get a satisfactory result.
 \section{Plan}
 \subsection{Image to Sentence}
-The first part of this problem is to generate a sentence based on the image. This sentence must contain the detail of this image, and it can describe this image.
+The first part of this problem is to generate a sentence based on the image. This sentence must contain the details of this image, and it can describe this image.
 
@@
 \section{Intermediate Result}
-We have built a temporary framework and consulted one expert about this problem. The expert thought it's a very good  and practical reasonable idea and gave some advices.
-We will soon try to use theano to implement our idea. Recent three weeks is the deadline of building a cpu so we don't have enough time to try our idea.
+We have built a temporary framework and consulted one expert about this problem. The expert thought it's a practical idea and gave some advice.
+We will soon try to use theano to implement our idea. Recent three weeks are the deadline of building a cpu so we don't have enough time to try our idea.
 \end{document}

### 2015-12-19 poem/load_data_config.py
doing

@@ -1,0 +1,67 @@
+from json import dumps
+
+
+word_dictionary = {}
+file_written = []
+word_cnt = {}
+
+with open("raw_train.data", "r") as f:
+    content = f.readline()
+    while content != "":
+        sentences = content.split("\n")[0].split("\t")
+        valid = True
+        for sentence in sentences:
+            if sentence.find("<") != -1:
+                valid = False
+        if valid:
+            poem = []
+            for sentence in sentences:
+                words = sentence.split(" ")
+                if len(words) != 5:
+                    continue
+                sentence_list = []
+                for word in words:
+                    if word not in word_dictionary:
+                        word_cnt[word] = (len(word_dictionary), 0)
+                        word_dictionary[word] = len(word_dictionary)
+                    sentence_list.append(word_dictionary[word])
+                    word_cnt[word] = (word_cnt[word][0], word_cnt[word][1] + 1)
+
+                poem.append(sentence_list)
+            if len(poem) > 0:
+                file_written.append(poem)
+        content = f.readline()
+
+word_cnt_list = []
+for i in word_cnt:
+    word_cnt_list.append(word_cnt[i])
+word_cnt_list = sorted(word_cnt_list, key = lambda a : -a[1])
+
+
+limited = 40
+new_word_dictionay = {}
+new_word_index = 1
+for i in word_cnt_list:
+    if i[1] <= limited:
+        new_word_dictionay[i[0]] = 0
+    else:
+        new_word_dictionay[i[0]] = new_word_index
+        new_word_index += 1
+
+for poem in file_written:
+    for sentence in poem:
+        for i in range(0, len(sentence_list)):
+            sentence[i] = new_word_dictionay[sentence[i]]
+temp = {}
+for i in word_dictionary:
+    if new_word_dictionay[word_dictionary[i]] != 0:
+        temp[i] = new_word_dictionay[word_dictionary[i]]
+
+word_dictionary = temp
+word_dictionary["unknown"] = 0
+
+with open("train.data2", "w") as f:
+    f.write(dumps(file_written, indent = 4))
+print "dictionary size is %s" % (str(len(word_dictionary)))
+with open("dictionary.data2", "w") as f:
+    f.write(dumps(word_dictionary, indent = 4))

### 2015-12-19 core/data/data.py
data commit

@@ -2,7 +2,8 @@ from json import loads, dumps
 import numpy as np
 import random
 import os
-
+import math
+import time
 class DataGenerator:
     def __init__(self, dir_, dictionary, img_path):
         with open(dir_, "r") as f:
@@ -188,3 +189,111 @@ class DataGeneratorFeature(DataGenerator):
         for i in range(0, batch_size):
             if self.hasNext():
                 self.next()
+
+
+class PoemDataGenerator:
+    def __init__(self, dir_, dictionary):
+        with open(dir_, "r") as f:
+            temp = loads(f.read())
+        self.rev_dictionary = {}
+        for i in dictionary:
+            self.rev_dictionary[dictionary[i]] = i
+        size = self.detectData(temp, self.rev_dictionary)
+        self.data = []
+        self.data_word_size = {i : 0 for i in range(len(dictionary))}
+        for poem in temp:
+            for i in range(3):
+                s = poem[i]
+                t = poem[i + 1]
+                p = self.calcSentenceProb(size, s) + self.calcSentenceProb(size, t)
+                print p
+                if p < 120000 * random.random():
+                    self.data.append((s, t))
+                    for z in s:
+                        self.data_word_size[z] += 1
+        calc_list = []
+        for i in self.data_word_size:
+            calc_list.append(self.data_word_size[i])
+        print max(calc_list)
+        time.sleep(3)
+        print calc_list
+        self.data_index = 0
+        self.word_dictionary_size = len(dictionary)
+        self.dictionary = dictionary
+
+    def calcSentenceProb(self, size, sentence):
+        ret = 0
+        for word in sentence:
+            cnt = size[word][1]
+            ret = ret + math.log(cnt) ** 5
+            # if cnt <= 100:
+            #     ret *= 100 / cnt
+            #     continue
+            # ret /= cnt / 100.0
+        return ret
+
+    def resetData(self):
+        self.data_index = 0
+
+    def shuffle(self):
+        random.shuffle(self.data)
+
+    def data(self):
+        return self.data[self.data_index]
+
+    def hasNext(self):
+        return self.data_index != len(self.data)
+
+    def next(self):
+        self.data_index += 1
+        return self.data[self.data_index - 1]
+
+    def calcData(self):
+        s = self.data[self.data_index][0]
+        t = self.data[self.data_index][1]
+
[…]

### 2015-12-22 paper.tex
papaer

@@
 Our approach is a combination of the above two aspects, we select two methods that performing well in corresponding aspects, and try to get a satisfactory result.
-\section{Plan}
-\subsection{Image to Sentence}
-The first part of this problem is to generate a sentence based on the image. This sentence must contain the details of this image, and it can describe this image.
+% \section{Plan}
+% \subsection{Image to Sentence}
+% The first part of this problem is to generate a sentence based on the image. This sentence must contain the details of this image, and it can describe this image.
 
-The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L.
+% The method we want to use here is proposed by Junhua Mao\footnote{ Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L.
 Yuille : Explain Images with Multimodal Recurrent Neural Networks.}.
@@
 
-\subsection{Translate and Extract}
-Now we get the sentence, as to generate the meaningful poetry, we need to extract keywords from the sentences.
+% \subsection{Translate and Extract}
+% Now we get the sentence, as to generate the meaningful poetry, we need to extract keywords from the sentences.
 We can use a translation process to deal the sentence and only use the words that appears in Chinese poetry dataset that we used in poem generator.
 
-\subsection{Poem generator}
-	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints.
+% \subsection{Poem generator}
+% 	The method we will use to generate poem is proposed by Mirella Lapata\footnote{Xingxing Zhang, Mirella Lapata : Chinese Poetry Generation with Recurrent Neural Networks.}.First, to create the first line of poem, We select all phrases corresponding to the users’s keywords and generate all possible combinations satisfying the tonal pattern constraints.
 We use a language model to rank the generated candidates and select the best ranked one as the first line in the poem.
 In implementation, we employ a character-based recurrent neural network language model.
-	And after that, we generate the rest poem lines with original lines.
+% 	And after that, we generate the rest poem lines with original lines.
 Convert lines $s_1$...$s_i$ into vectors $v_1$...$v_i$ with a convolutional sentence model (CSM).
@@
 %-------------------------------------------------------------------------
-\section{Dataset}
-The dataset we used is IAPR TC-12 dataset, which used to training the model that explain image.
 
-The other is Chinese Poetry corpus to train for the generate part.
-\section{Intermediate Result}
-We have built a temporary framework and consulted one expert about this problem. The expert thought it's a practical idea and gave some advice.
-We will soon try to use theano to implement our idea. Recent three weeks are the deadline of building a cpu so we don't have enough time to try our idea.
+\section{Approach}
+The way we solve this project is to build three seperate parts.
+\begin{itemize}
+\item image feature extractor
+\item translation
+\item poem generator
+\end{itemize}
+
+These three part will process the data one by one and finally generate the poem.
+
+\subsection{Extractor}
+The first part is extracting the feature from image, and these features can be transformed to translation part and poem generator part to generate the poem.
+
+To extract features from image, we use a 16-layer VGGnet trained for ImageNet, which performs well in many experiment about image proccessing. 
+However, the result of this model is not good enough for us to make the poem, for the thing needed by the poem can’t be transformed from the image features directly.
+Poem generator need more detailed information.
+
+As to make it more suitable for our target, we fine-tuning it on another problem.
+We have built a model to explain images with english sentences for IAPRTC12 datasets.
+In the dataset, each data has sentences descriptions for context of it.
+We hope it will lead VGGnet to extract important context of the image, and these contexts are the major things that lead the poem generator to generate the poem.
+The specific model architecture is imspired from Junhua Mao’s work[].
+
+This model is combined by two part.
+First part extracts features from images, and we use our VGGnet.
+Second part is based on recurrent neural network to generate sentences with image features and word vectors.
+In practical, our sentence generation model is different from Junhua Mao’s work[], shown in figure 1.
+We encode input words with two FullyConnected layers, put it from a sparse vector to a dense vector.
+And then put it into a LSTM layer to generate next word’s dense representation.
+After that, we joint the output of LSTM layer, FullyConnected layer and image features, as the input of next layer.
+Finally we use a FullyConnected layer and a Softmax layer to decode the vector, transform it from a dense vector to a sparse word representation.
+
+\subsection{Translation}
+In poem generator part, we want to create the next sentence by the last sentence, so that what we need to provide with this generator is the first sentence of poem and it will create the rest part of poem.
+However, how to translate the feature extracted from the image into the first poem is a difficult thing.
+
+The solution of this puzzle is that we simply make the features from the image into one meaningless sentence, so that this meaningless sentence will lead the generator to create the first sentence.
+
+The translation part will translate the features got from extractor into one meaningless sentence.
+This sentence may be weird of it's order of word but contains enough information of the corresponding image.
+
+具体过程是啥？？？？？？？？？？？
+
+\subsection{Poem generator}
+
+\begin{figure}[t]
+\begin{center}
+   \includegraphics[width=0.8\linewidth]{report/poem_layers.png}
+\end{center}
+   \caption{The network of poem part.}
+\label{fig:poem_layer_network}
+\end{figure}
+
+As the first sentence has been created by the generator, we can use our model to generate the following three sentences.
+We use RNN (recurrent neural network) to train this poem generator model. The reason why we choose this model is that RNN model is wonderful to train the things that can be determined by the previous.
+
+We only train the poem which the length of sentence of is 5, this ensure the backpropagation won’t be effectless (the derivate won’t be too small to change the model).
+
+The reason that we don’t use LSTM ( Long Short Term Memory networks ) is it’s much more efficient, and we are constrained by the GPU, we only have two laptops to train our models.
+
+The train data is a sentence and output a single word represent the following word of this sentence.
+
+For we don’t have enough computing resource to train our model, we simplify our model.
+
+The first layer is input layer, as a one hot decoder layer.
+The sentence will be decoded here to generate a five vectors that encoded from the origin sentence.
+The one hot decoder is a vector with only one element is 1, and else are 0.
+If the input containing 5 words is $[x_{0}, x_{1}, x_{2}, x_{3}, x_{4}]$.
+Each $x_{i}, 0 <= i <= 4$ is the a word, and will be transformed into
+\begin{center}
+$y_{i} = [0, 0, 0, ... 0, charSet[x_{i}], 0, 0, ... , 0, 0, 0]$
+\end{center}
+
+Here charSet is the charset of all poems, we map a single $word$ into a number $charSet[x_{i}]$.
+After this layer, we get a vector $output_{5, size(charSet)}$, and this vector will transform into the RNN layer.
+
+The next layer is a RNN layer, use to calculate the following word based on the input sentence.
+We only use the last time of RNN’s output as the output of layer, and process it into third layer.
+This output can calculate the output based on input (five words).
+
+The layer has three parameters $w, h, b$, in $0 <= step_{i} <= 4$, it will calculate the $input_{5, size(charSet)}$ as follow.
+\begin{center}
+    $result_{i} = w * input_{i} + h * result_{i - 1} + b$
+\end{center}
+
+The third layer is a fclayer.
+In this layer we map the output from the rnn layer to the vector of the same size of the word set.
+We don’t use any activation function because it’s enough to train the good sentence without any activation function.
+
+The last layer is a softmax layer, we use softmax layer for two reasons.
+
+\begin{itemize}
+\item Generating proper loss function to update this layer.
+\item It can generate the probability of next word.
+For the rhythm purpose, we should decide the next word not only by the probability, but also follow the rule of rhythm which means the fourth sentence’s last word should match with the second sentence’s last word.
+Softmax layer is the best choice as it can calculate each word’s probability to be the next word.
+We only need to pick up the word that satisfy the rule of rhythm and has the maximum probability.
+\end{itemize}
+
+\section{Experiment}
+
+\subsection{Dataset}
+The dataset we used for poem generator is Tang Poems, Song Poems, Song Ci, Ming Poems, Qing Poems, and Tai Poems.
+It contains 78859 poems, and can be downloaded here.
+We only use quatrains and five words per sentence to train, validate and test.
+Finally the total poems are 11098.
+
+\begin{figure}[t]
+\begin{center}
+   \includegraphics[width=0.8\linewidth]{report/frequent.png}
+\end{center}
+   \caption{The frequent of word in dataset.}
+\label{fig:frequent}
+\end{figure}
+
+During the training, we find some some words appear too often, like no.
+These words appear more than 40\% of dataset, which will influence the RNN layer to output this word too often.
+We want to prevent from this thing happening, so we filter the dataset and choose only 2000 poems to be the training set.
+To increase the diversity of words appeared in sentences, we set the evaluate function.
+Use this function, we select part poems from dataset and ensure the word frequency are most equal. See . Each poem will generate 15 data, for example .
+Origin poem 春眠不觉晓，处处闻啼鸟
+Input   output
+春眠不觉晓 处
+眠不觉晓处 处
+不觉晓处处 闻
+觉晓处处闻 啼
+晓处处闻啼 鸟
+The size of validate set is 100, and test size is 100. 
+The way of train the model is quite inter
+
+\begin{itemize}
+\item[*] a
+\item[*] b
+\end{itemize}
+
 \end{document}

### 2015-12-22 paper.tex
paper

@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
-
 \usepackage{cvpr}
@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{0} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \section{Related Work}
-	Generating poem is popular in recent years, and there are abundant research on it.
+    Automated poem generation are popular in recent years, and there are abundant research on it.
 On the other hand, explaining image with words has also made great progress after deep learning is widely used.
+And as recurrent neural network performs well in processing sequence data, more and more researchers use it (or its varient) trying to solve different problems.
+
+    Because of recurrent neural network’s architecture, prior information of sequence can be used by latter computation, which is a good character for people to process sequence data.
+Some researcher now use it explain image with sentences.
+They put images as input and generate sentences by model based on recurrent neural network.
+It is much easier to implement than original language model method.
+
+    Poem generation is same as above problem somehow.
+In recent summaries, complex recurrent neural network performs better than original method, and this method has more expandability, like generating Chinese couplet or generate other language poems.
+Besides, researchers use other methods to improve the performance of RNN model, like statistical machine translation and related text-generation applications such as summarization.
+
     Our approach is a combination of the above two aspects, we select two methods that performing well in corresponding aspects, and try to get a satisfactory result.
+
 % \section{Plan}
@@
 \subsection{Extractor}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.7\linewidth]{report/first_model.jpg}
+\end{center}
+   \caption{The network of first model.}
+\label{fig:first_layer_network}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.7\linewidth]{report/second_model.jpg}
+\end{center}
+   \caption{The network of second model.}
+\label{fig:second_layer_network}
+\end{figure*}
+
 The first part is extracting the feature from image, and these features can be transformed to translation part and poem generator part to generate the poem.
 
-To extract features from image, we use a 16-layer VGGnet trained for ImageNet, which performs well in many experiment about image proccessing. 
+\subsubsection{Fine-tuning feature extractor by image description generation}
+
+To extract features from image, we use a 16-layer VGGnet\footnote{Model can be found here https://gist.github.com/ksimonyan/
+
+211839e770f7b538e2d8\#file-readme-md} trained for ImageNet, which performs well in many experiment about image proccessing.
 However, the result of this model is not good enough for us to make the poem, for the thing needed by the poem can’t be transformed from the image features directly.
@@
 As to make it more suitable for our target, we fine-tuning it on another problem.
-We have built a model to explain images with english sentences for IAPRTC12 datasets.
-In the dataset, each data has sentences descriptions for context of it.
+We want to build a network to explain images and create English sentences based on the image.
+So we use IAPRTC12 datasets.
+In IAPRTC12 dataset, each data has several sentence descriptions.
 We hope it will lead VGGnet to extract important context of the image, and these contexts are the major things that lead the poem generator to generate the poem.
-The specific model architecture is imspired from Junhua Mao’s work[].
+The specific model architecture is inspired from Junhua Mao’s work\footnote{Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L.
+Yuille : Explain Images with Multimodal Recurrent Neural Networks.}.
 
-This model is combined by two part.
-First part extracts features from images, and we use our VGGnet.
-Second part is based on recurrent neural network to generate sentences with image features and word vectors.
-In practical, our sentence generation model is different from Junhua Mao’s work[], shown in figure 1.
+This model consists of two parts.
+First part extracts features from images, and we use our VGGnet here.
+Second part is based on recurrent neural network to generate image descriptions based on the image features got from the first part and the word vector generated before in this part.
+Actually, our description generation model is different from Junhua Mao’s work, shown in figure 1.
 We encode input words with two FullyConnected layers, put it from a sparse vector to a dense vector.
@@
 
+As shown in figure 1, first we encode input words with two FullyConnected layers, transform it from a sparse word representation to a dense vector, we hope it can extract implication from words.
+
+\begin{center}
+$
+y = W * x + b
+$
+\end{center}
+
+And then put the dense vector into a LSTM layer to generate next word’s representation. The formula of specific LSTM layer implement is:
+\begin{center}
+$
+i_{t} = Sigmoid(W_{input\_gate} * x_{t} + H_{input\_gate} * h_{t-1} + $
+
+$b_{input\_gate})
+$
+
+$
+o_{t} = Sigmoid(W_{output\_gate} * x_{t} + H_{output\_gate} * h_{t-1} + b_{output\_gate})
+$
+
+$
+f_{t} = Sigmoid(W_{forget\_gate} * x_{t} + H_{forget\_gate} * h_{t-1} + b_{forget\_gate})
+$
+
+$
+c_{t} = f_{t} * c_{t-1} + i_{t} * Tanh(W_{cell\_store} * x + H_{cell\_store} * h_{t-1} + b_{cell\_store})
+$
+
+$
+h_{t} = o_{t} * Tanh(c_{t})
+$
+\end{center}
+
+Here $x_{t}$ is the input of LSTM layer, $i_{t}$, $o_{t}$ and $f_{t}$ are LSTM layer’s three gate(input gate, output gate and forget gate), and $c_{t}$ is the storage, $h_{t}$ is the output of the LSTM layer.
+From above formulas we can see, the increase of exponential in derivative calculation is much slower than RNN layer.
+As proved in many experiments, Long-Short Term Memory performs much better than recurrent neural network on processing long sequence data, although training it takes much time.
+
+After that, we joint the output of LSTM layer, FullyConnected layer and image features, as the input of next layer.
+This is inspired from Junhua Mao’s work, but not same as their method, we did not simply accmulate three outputs, but concatenate them in our model.
+
+\begin{center}
+$
+y_{fc} = \{y_{fc}^1,y_{fc}^2, ..., y_{fc}^n\}
+$
+
+$
+y_{rnn} = \{y_{rnn}^1,y_{rnn}^2, ..., y_{rnn}^m\}$
+
+$y_{img} = \{y_{img}^1,y_{img}^2, ..., y_{img}^k\}$
+
+$y_{m} = \{y_{fc}^1,y_{fc}^2, ..., y_{fc}^n,y_{rnn}^1,y_{rnn}^2, ..., $
+
+$y_{rnn}^m,y_{img}^1,y_{img}^2, ..., y_{img}^k\}$
+
+\end{center}
+
+Here $y_{fc}$ is the output of word encoder(the second FullyConnected layer), $y_{rnn}$ is the output of LSTM layer, $y_{img}$ is the features extract by our VGGnet, and $y_{m}$ is the vector concatenated by three outputs.
+
+The VGGnet we used here is not same as the original model, we remove the last two layers from VGGnet and use its last but one’s FullyConnected layers’ output as our image features.
+
+At last, we choose a FullyConnected layer and a Softmax layer as the decoder to transform LSTM’s output to a sparse word representation.
+
+Finally, we get the first model, this model will fine-tuning our VGGnet model to make it work of extract feature not detection nor classification.
+
+\subsubsection{Train feature extractor}
+As the VGGnet was fine-tuninged, we build the second model to generate keywords from image, which will be used to generate our poem.
+This model is much easier than first as shown in figure 2.
+Its architecture is same as original VGGnet, but here we trained for different dataset, which are dealed from IAPRTC12 by us.
+
+% \begin{figure}[t]
+% \begin{center}
+%    \includegraphics[width=0.8\linewidth]{report/first_model.jpg}
+% \end{center}
+%    \caption{The network of first model.}
+% \label{fig:first_layer_network}
+% \end{figure}
+
+% \begin{figure}[t]
+% \begin{center}
+%    \includegraphics[width=0.8\linewidth]{report/second_model.jpg}
+% \end{center}
+%    \caption{The network of second model.}
+% \label{fig:second_layer_network}
+% \end{figure}
+
 \subsection{Translation}
 In poem generator part, we want to create the next sentence by the last sentence, so that what we need to provide with this generator is the first sentence of poem and it will create the rest part of poem.
-However, how to translate the feature extracted from the image into the first poem is a difficult thing.
+However, how to translate the keywords extracted from the image into the first poem is not an easy thing.
 
-The solution of this puzzle is that we simply make the features from the image into one meaningless sentence, so that this meaningless sentence will lead the generator to create the first sentence.
+The solution of this puzzle is that we translate make the keywords from the image into Chinese words, then we search these words in our poem database and choose the Chinese character appeared in both keywords and poem database to produce a meaningless sentence.
+This sentence may be weird of it's order of word but contains enough information of the corresponding image.
 
 The translation part will translate the features got from extractor into one meaningless sentence.
-This sentence may be weird of it's order of word but contains enough information of the corresponding image.
-
-具体过程是啥？？？？？？？？？？？
+This sentence may be weird of its sequence of words but contains enough information of the corresponding image.
+Then this sentence will be sent to the poem generator to generate the following sentences.
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
 \begin{center}
-   \includegraphics[width=0.8\linewidth]{report/poem_layers.png}
+   \includegraphics[width=0.35\linewidth]{report/poem_layers.png}
 \end{center}
@@
 \label{fig:poem_layer_network}
-\end{figure}
+\end{figure*}
 
@@
 
-Here charSet is the charset of all poems, we map a single $word$ into a number $charSet[x_{i}]$.
+Here $charSet$ is the charset of all poems, we map a single $word$ into a number $charSet[x_{i}]$.
 After this layer, we get a vector $output_{5, size(charSet)}$, and this vector will transform into the RNN layer.
@@
 \section{Experiment}
+\subsection{Dataset}
+\subsubsection{Image dataset}
+We use IAPRTC12\footnote{It can be found by http://www.imageclef.org/photodata.} dataset to fine-tuning our VGGnet.
+It consists of 20,000 still natural images taken from locations around the world and comprising an assorted cross-section of still natural images.
+And every image has some useful labels, one of them is a short description of the image, which is suitable for our target.
 
-\subsection{Dataset}
+For the first model, we directly use the images and the descriptions in IAPRTC12, but some descriptions may too long to learn useful information for our model.
+So that we only choose the first sentence of the description as our input word sequence.
+The short sentence can make train better.
+
+Then we make some change on dataset for our features extractor's second model.
+Second model is trained for extracting keywords from image, so we extract the keywords from the descriptions by remove useless words.
+
+The dataset contains more than 30000 images, we use all of these images to train the model.
+
+\subsubsection{Poem dataset}
 The dataset we used for poem generator is Tang Poems, Song Poems, Song Ci, Ming Poems, Qing Poems, and Tai Poems.
-It contains 78859 poems, and can be downloaded here.
+It contains 78859 poems, and can be downloaded\footnote{The data used in our experiments can be downloaded from http://homepages.inf.ed.ac.uk/mlap/index.
+php?page=resources.} here.
 We only use quatrains and five words per sentence to train, validate and test.
@@
 \end{center}
-   \caption{The frequent of word in dataset.}
+   \caption{The frequent of word in dataset. The largest number is 3361. More than 80\% words appear less than 200 times.}
 \label{fig:frequent}
@@
 
-During the training, we find some some words appear too often, like no.
-These words appear more than 40\% of dataset, which will influence the RNN layer to output this word too often.
+During the training, we find some words appear too often, like no.
+These words appear more than 30\% of dataset, which will influence the RNN layer to output this word too often.
+It's obviously that more than 80\% word appear less that 3\% of poem, and this word can't be studied well.
 We want to prevent from this thing happening, so we filter the dataset and choose only 2000 poems to be the training set.
 To increase the diversity of words appeared in sentences, we set the evaluate function.
-Use this function, we select part poems from dataset and ensure the word frequency are most equal. See . Each poem will generate 15 data, for example .
-Origin poem 春眠不觉晓，处处闻啼鸟
-Input   output
-春眠不觉晓 处
-眠不觉晓处 处
-不觉晓处处 闻
-觉晓处处闻 啼
-晓处处闻啼 鸟
-The size of validate set is 100, and test size is 100. 
-The way of train the model is quite inter
+\begin{center}
+    $poem=[sentence_{0..3}]$
 
-\begin{itemize}
-\item[*] a
-\item[*] b
-\end{itemize}
+    $sentence_{i}=w_{i, 0..4}$
+    $F(sentence_{i}) = \sum_{i=0}^{4}(log(count[w_{i, i}]))^5$
+    $F(poem)=\sum_{i=0}^{3}{F(sentence_{i})}$
+\end{center}
+
+Here $poem$ is composed by 4 sentences and $sentence$ is composed by 5 words.
+The probability of adding this poem into train set is $F(poem)$.
+$count$ is the frequent of word appearing in the dataset.
+We set the $standard$ of the poem, if $standard*random(0, 1) < F(poem)$ then we add this poem into train set.
+Using this function, we select part poems from dataset and ensure the word frequency are most equal.
+
+At last, we select 2000 poems, and the biggest frequency is 238, which is drastically reduced from 30\% to 12\%.
+
+Each poem will generate 15 data, using 5 continuous words to train the next word.
+These continuous words can be selected from two sentences, the purpose of this is making RNN to learn the relationship from two sentences.
+This feature will be found in the example part.
+
+\begin{figure}[t]
+\begin{center}
+   \includegraphics[width=0.8\linewidth]{report/data_generate.png}
+\end{center}
+   \caption{How to convert 2 sentences into 5 data points.}
+\label{fig:data_generator}
+\end{figure}
+
+The size of validate set is 100, and test size is 300. It's difficult to judge a poem. What we can do is judge it from people respect, and the test data set's loss function accuracy both.
+\subsection{Training}
+\subsubsection{Extractor training}
+During our training, lot's of problem occured.
+
+In English, $a$ this word will appear too often, so at the very beginning, what we trained from the first model is a sentence like $a,a,a,a,a,a,a,a,a$.
+To solve this problem, we change the order of train data, and feed the data that don't contain a in the description.
+After trained several time, we put rest data and train together.
+
+The length of English sentence is too long to train.
+Chinese poem only has five words per sentence so it's easy to use RNN to train the model.
+We have to select some sentences not too long to train the model.
+In this step, we might lose some information as we don't use very long sentence to train our model.
+
+\subsubsection{Poem training}
+During our training process, the biggest problem is lack of GPU, so we only train our models with CPU.
+It's really slow for CPU to train a large models.
+At the very beginning, we want to use LSTM model instead of RNN, however each data point will cost 1 second, which is unacceptable.
+So we change to RNN model.
+
+Lack of GPU also cause a problem, we can't feed too many data, for the model is not complex enough to study.
+As mentioned before, we only train 2000 data in one time, and we totally have 11000 data.
+So we train this model 5 times, each time we give only 2000 data to train.
+Besides, we dynamically change the learning rate.
+
+We use three major different way to train the model.
+The result is pretty well.
+Although the best model's accuracy is 43\%, the word that called ShiCi like people, boat, tree can't be trained well, because different poem describe different things, we can't infer the things from the previous sentence.
+The conjunction words like no, where, also can trained pretty weel.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|l|l|}
+\hline
+Training way & Loss function & Test accuracy \\
+\hline\hline
+All poem train & 5.844 & 8\%\\
+5 times train & 4.392 & 21\%\\
+5 times train + change lr & 1.878 & 43\%\\
+\hline
+\end{tabular}
+\end{center}
+\caption{The result of three different training ways.}
+\end{table}
+
+\subsection{Example}
+Using our model, we can feed in a image and make one poem. Here is an example.
+
+\begin{figure}[t]
+\begin{center}
+   \includegraphics[width=0.5\linewidth]{report/example1.jpg}
+   \includegraphics[width=0.3\linewidth]{report/poem1.png}
+\end{center}
+   \caption{example 1.}
+\label{fig:example1}
+\end{figure}
+
+\begin{figure}[t]
+\begin{center}
+   \includegraphics[width=0.5\linewidth]{report/example2.jpg}
+   \includegraphics[width=0.3\linewidth]{report/poem2.png}
+\end{center}
+   \caption{example 2.}
+\label{fig:example2}
+\end{figure}
+
+In example1, we can find that it occurs like North and South these two words, which represent the model do learn something from the origin poem.
+In image 1, it has tree and house so the poem can find something about these two main features.
+
+In example2, there is a river and a boat, and the weather is fog, so the first sentence contains these feature. The last sentence will show the feathre boat in the image.
+
+These two examples all show that our model have enough ability to make the poem based on the given image.
+
+\section{Conclusion}
+    In this paper we have presented a model for Chinese poem generation based on given image.
+The first part is to extract information and features from the image and the second part is to generate one poem based on the given information.
+
+    We really learn lot's of thing from this project, like the how to train RNN model and how use others model to train our own model and the usage of caffe and theano.
+
+    The final result is pretty well, although our poem is not good enough compared with the ancients, we still believe the study ability of computer is much more higher.
+If we have better computing resource and time, we can train a larger network, which will work pretty better.
+
+    There are lots of things that we can improve.
+There is no transition between two sentences, and there is no pattern of the poem.
+It might be better if the poem can follow one pattern decided by the ancients.
+The image feature extracting is also not perfect.
+If it's possible, the best way is to extract the feature directly from the image, not by one classification network.
+We can also put more type of poem (e.g., Engish sonnets or Japanese haiku) into our train model, or add the new language into this generator.
+
+    This project make us know the super power of neural network in generation problem, not only in classification problem.
+We hope in the future, we will have more chances to do the research in neural network.
+
+\section{References}
+\begin{thebibliography}{1}\itemsep=-1pt
+
+\bibitem{1}
+Authors.
+\newblock Junhua Mao, Wei Xu, Yi Yang, Jiang Wang, Alan L. Yuille 
+\newblock Explain Images with Multimodal Recurrent Neural Networks.
+
+\bibitem{2}
+Authors.
+\newblock Xingxing Zhang, Mirella Lapata
+\newblock Chinese Poetry Generation with Recurrent Neural Networks.
+
+\bibitem{3}
+Authors.
+\newblock Wenwei Liu. 
+\newblock 1735. ShiXueHanYing.
+
+\bibitem{4}
+Authors.
+\newblock A.Frome, G.S.Corrado, J.Shlens, S.Bengio, 
+\newblock J.Dean, T.Mikolov, etal.Devise
+\newblock Adeepvisual-semantic embedding model.
+
+\bibitem{5}
+Authors.
+\newblock T. Mikolov, M. Karafia ́t, L. Burget, 
+\newblock J. Cernocky`, S. Khudanpur
+\newblock Recurrent neural network based language model.
+
+\bibitem{6}
+Authors.
+\newblock K. Barnard, P. Duygulu, D. Forsyth, N. De Freitas, 
+\newblock D. M. Blei, and M. I. Jordan
+\newblock Matching words and pictures.
+
+\end{thebibliography}
 

### 2015-12-22 layers/layers.py
final ckl

@@ -36,7 +36,7 @@ class LayerBase(object):
     def __init__(self, **kwargs):
         super(LayerBase, self).__init__()
         self.learning_rate = 0.001
-        self.weight_decay = 0.000001
+        self.weight_decay = 0.00001
         self.dropout_prob = None
         if 'learning_rate' in kwargs:
             self.learning_rate = kwargs['learning_rate']
@@ -355,7 +355,7 @@ class ColumnWiseSoftmax(LayerBase):
     def cost(self, y_in, y_truth):
         x = y_in - y_in.max(axis=2, keepdims=True)
         log_prob = x - T.log(T.exp(x).sum(axis=2, keepdims=True))
-        res = -(y_truth * log_prob).sum(axis=[2,3]).mean()
+        res = -(y_truth * log_prob).sum(axis=[2]).mean()
         return res
 
     def get_params(self):

### 2015-12-22 layers/model_feature_v1.py

@@ -1,0 +1,245 @@
+from layers import *
+import theano
+import theano.tensor as T
+import numpy as np
+from json import loads, dumps
+import sys
+import os
+sys.path.append("../core")
+from data.data import DataGenerator, DataGeneratorFeature
+from time import localtime
+from IPython import embed
+
+def printTime():
+    t = localtime()
+    print "time is %d:%d:%d"%(t[3], t[4], t[5])
+
+word_dictionary, data_generator = (None, None)
+
+def local_fprop(image_feature, y_truth): # x = sentences  y_truth is [[][]]
+    global word_dictionary
+
+    # fc0 = ColumnWiseFullyConnected(
+    #         input_dim=len(word_dictionary),
+    #         output_dim=512,
+    #         nonlinearity=tanhFunc,
+    #         # dropout_prob=0.2,
+    #         name = "fc0"
+    #     )
+
+    # fc1 = ColumnWiseFullyConnected(
+    #     input_dim=512,
+    #     output_dim=256,
+    #     nonlinearity=tanhFunc,
+    #     # dropout_prob=0.2,
+    #     name = "fc1"
+    #     )
+
+
+    multimodal_image = ColumnWiseFullyConnected(
+            input_dim=4096,
+            output_dim=1024,
+            nonlinearity=reluFunc,
+            name = "multimodal_image"
+    )
+
+    multimodal_image2 = ColumnWiseFullyConnected(
+            input_dim=1024,
+            output_dim=256,
+            nonlinearity=reluFunc,
+            dropout_prob=0.2,
+            name = "multimodal_image2"
+    )
+
+
+    fc2 = ColumnWiseFullyConnected(
+        input_dim=256,
+        output_dim=len(word_dictionary),
+        nonlinearity=identityFunc,
+        dropout_prob=0.2,
+        name = "fc2"
+        )
+
+#    euc0 = EuclideanLoss(
+#        name = "euc"
+#    )
+    softmax = ColumnWiseSoftmax(name = 'softmax')
+
+
+    # embeded1_out = fc0.fprop(x)
+    # embeded2_out = fc1.fprop(embeded1_out)
+    multimodal_image_out = multimodal_image.fprop(image_feature)
+    multimodal_image_out2 = multimodal_image2.fprop(multimodal_image_out)
+    # multimodal_out = embeded2_out + multimodal_image_out
[…]

### 2015-12-22 layers/model_rmsprop.py

@@ -107,20 +107,25 @@ def local_fprop(x, y_truth, image_feature): # x = sentences  y_truth is [[][]]
         multimodal_image
     ]
 
+    # L2 regularization
+    for layer in layers:
+        for p in layer.get_params():
+            my_cost += (p**2).mean()
+
     # RMSprop
-    rho = 0.9
-    epision = 1e-6
+#    rho = 0.9
+#    epision = 1e-6
     for layer in layers:
         for p in layer.get_params():
             lr = layer.learning_rate
             wd = layer.weight_decay
             g = T.grad(cost=my_cost, wrt=p)
-            p_delta = theano.shared(p.get_value() * 0.)
-            p_delta_new = rho * p_delta + (1 - rho) * g**2;
-            gradient_scaling = T.sqrt(p_delta_new + epision)
-            g = g / gradient_scaling
-            my_update.append((p_delta, p_delta_new))
-            my_update.append((p, p * (1 - wd) - lr * g))
+#            p_delta = theano.shared(p.get_value() * 0.)
+#            p_delta_new = rho * p_delta + (1 - rho) * g**2;
+#            gradient_scaling = T.sqrt(p_delta_new + epision)
+#            g = g / gradient_scaling
+#            my_update.append((p_delta, p_delta_new))
+            my_update.append((p, p - lr * (p * wd + g)))
 
     return my_out, my_cost, my_update, layers
 
@@ -151,8 +156,8 @@ if __name__ == '__main__':
     output, cost, update, layers = local_fprop(data, label, image_feature)
     train_func = theano.function(inputs=[data, label, image_feature], outputs=[output, cost], updates=update,
             on_unused_input='warn', allow_input_downcast=True)
-    test_func = theano.function(inputs=[data, label, image_feature], outputs=[output, cost],
-            on_unused_input='warn', allow_input_downcast=True)
+#    test_func = theano.function(inputs=[data, label, image_feature], outputs=[output, cost],
+#            on_unused_input='warn', allow_input_downcast=True)
     
     mtr = Monitor(layers, load_path = args.load_path, save_path = './train_log_rmsprop')
     if args.load_path:
@@ -181,10 +186,8 @@ if __name__ == '__main__':
                     print cost
                     print data_generator.translate(output)
                     print data_generator.translate(train_data_sentence)
-                if index == cnt:
-                    break
             batch_cost = sum(cost_set)/len(cost_set)
             print 'current batch cost = {}'.format(batch_cost)
[…]

### 2015-12-22 layers/monitor.py

@@ -10,7 +10,6 @@ class Monitor(object):
     
     def load(self):
         assert not self.load_path == None, self.load_path
-        assert os.path.exists(self.load_path), self.load_path
         for layer in self.layers:
             layer.load_data(self.load_path)
 
